\huge A Usability Evaluation of Tor Launcher

### 2016-10-28 pets2017-paper/pets2017-paper.tex
minor word tweaks in recommendation and limitations

\section{Recommendations}
\label{recommendations}
We do believe that adopting our design will help save users time when connecting to Tor. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made. Some of our changes may have little or negative effect. Additionally, we recognize equivalent (or more impactful!) changes could be made in place of ours. Therefore, we do not recommend specific changes, but offer some suggestions based on what we learned: \\

@@

Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}. We are aware that our participants were likely motivated differently compared to real users. We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward. If true, this makes our results are a conservative estimate of the current problems.

@@

Our experiment did not directly test more advanced tasks. Our simulated environments did not require users to configuring a proxy or to get a custom bridge. From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how or why they do.

We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent. Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all testing conditions equally.

>>>>

\section{Recommendations}
\label{recommendations}
We do believe that adopting our design will help save users time when connecting to Tor. But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made. Some of our changes may have little or negative effect. Additionally, we recognize equivalent (or more impactful!) changes could be made in place of ours. Therefore, we do not recommend specific changes, but offer some suggestions for Tor Launcher's GUI based on what we learned: \\

@@

Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}. We are aware that our participants were likely motivated differently compared to real users. We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward. If true, this makes our results are a conservative estimate of the current usability problems.

@@

Our experiment did not directly test more advanced tasks. Our simulated environments did not require users to configuring a proxy or to get a custom bridge. From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how much they do.

We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent. Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
